\textls[-0]{\thetitle}

### 2023-03-15 related-work.tex
tweak

All of these approaches are largely extra\-linguistic, in that they work
within the confine of the language offered by a proof assistant, which
comes with trade-offs.
On the one hand,
they can be conveniently distributed as libraries, and the encoding can
be more easily adapted for new purposes.
For example, MTC~\cite{delaware2013} has been applied to implementing
composable program adverbs~\cite{liwei2022} and been adapted to allow
unanticipated feature extensions that require type changes
\cite{delaware2013b,vdr2022intrinsically}.

>>>>

All of these approaches are largely extra\-linguistic, in that they work
within the confine of the language offered by a proof assistant, which
comes with trade-offs.
On the one hand,
they can be conveniently distributed as libraries, and the encoding can
be more easily adapted for new purposes.
For example, MTC has been applied to implementing
composable program adverbs~\cite{liwei2022} and been adapted to allow
feature extensions, such as reference cells and exceptions, that require type changes
\cite{delaware2013b,vdr2022intrinsically}.
